\section*{Signature}

There are existing platforms which offer similar features indeed, for instance:

\begin{itemize}
    \item \textbf{URLVoid} can:
    \begin{itemize}
        \item Check the reputation and trust level of a website or domain.
        \item Provide information on IP address, server location, ASN, WHOIS details, and domain creation date.
        \item Allow viewing of website screenshots.
        \item Include network tools such as DNS lookup, ping, and traceroute.
    \end{itemize}

    \item \textbf{CheckPhishing} can:
    \begin{itemize}
        \item Scan URLs/websites in real time.
        \item Capture screenshots, extract DOM data, and apply natural language and image analysis.
        \item Offer procedures or options to request removal of detected phishing pages.
        \item \textbf{Malwarebytes} blocks phishing, malware/ransomware sites, malicious IPs/URLs, and inbound or outbound network threats.
    \end{itemize}
\end{itemize}


        
However, those websites/app’s functionalities work individually (none can all check the safety of a website in real-time via text input\footnote{ text input refers to getting a link/URL from a user's input on the search bar and from moving the mouse point to link/URL.} and image input\footnote{image input refers to getting a link/URL from a user's screenshot of the website which contains the website’s link/URL itself (most likely extracting text from image).}, provide website’s information, allow users to preview websites, suggest other similar websites which are reliable, and background process), which sometimes cause inconvenience or time-consuming for users. Conversely, our team combines all of those mentioned features into a single, complete product, providing users with maximum convenience, which we have found to be largely absent in most current offerings.
