\section{Problem}
\subsection{Background}
\textbf{Cyber-attacks}, defined as illegal attempts to compromise computer systems or steal sensitive information via the Internet, have become a critical global issue. With the rapid growth of online services and digital platforms, users are increasingly exposed to various forms of cyber threats. Among these threats, phishing websites and malware-infected web pages are particularly prevalent due to their ability to exploit both technical vulnerabilities and human trust.

The situation is especially concerning in Vietnam. According to recent reports, approximately 20\% of Internet users in Vietnam are exposed to web-based threats\cite{vov2024}. In 2024 alone, more than 19.8 million web-based cyber threat incidents were recorded nationwide\cite{dtinews2025}. As a result, the total financial damage caused by online scams was estimated to reach 18.9 trillion VND\cite{vietnamnet2025}. These figures demonstrate that web-based cyber threats pose not only technical risks but also significant economic consequences for individuals and society.


One of the most common attack methods involves \textbf{phishing websites} designed to steal personal data, banking credentials, and other sensitive information.

\subsection{Limitation Of Existing Solutions}
To mitigate the risks associated with malicious websites, various website-checking tools and antivirus solutions have been developed. However, many existing solutions still present notable limitations. Some tools require paid subscriptions, while others consume substantial system resources or provide incomplete evaluations by focusing solely on a single aspect of website safety, such as blacklist-based detection. Consequently, these solutions may be inconvenient or inaccessible for everyday users, particularly those without technical expertise.